% --------------------------------------------------
% @author Guillaume Seren
% source  https://github.com/GuillaumeSeren/CurriculumVitae
% file    GuillaumeSeren_en.tex
% Licence GPLv3
%
% Latex main file.
% --------------------------------------------------
%!TEX TS-program = xelatex

\documentclass[10pt,a4paper,sans]{moderncv}

\usepackage{GuillaumeSeren}
% personal data
\firstname{Guillaume}
\familyname{Seren}
\title{DevOps / Linux Engineer}
\email{guillaumeseren@gmail.com}
\extrainfo{%
  \linkedin~\httplink{https://www.linkedin.com/in/GuillaumeSeren}\\%
  \github~\httplink{https://github.com/GuillaumeSeren}\\%
Permis B%
}
\begin{document}

\makecvtitle

% Stuff we want to add:
% * 

\section{Summary}
\begin{center}
Dedicated and seasoned technology leader with a rich 16-year career,\\
seamlessly blending an 8-year foundation in software development,\\
with an additional 8 years of experience in DevOps.\\
I have consistently demonstrated a passion for problem solving\\
automation, streamline processes, and deliver robust solutions.
\end{center}

\section{Technical Skills}
\subsection{Linux}
\cvlistitem{Distros: Gentoo, Nixos, Arch, Debian, Centos}
\cvlistitem{Packaging: Create custom version of a program for various distros}
\cvlistitem{Network: iptables, tcpdump, netcat, nmap, socat}
\cvlistitem{Load balancer: l4 (keepalived), l7 (HAProxy)}
\cvlistitem{VPN: Wireguard, OpenVPN}
\cvlistitem{Filesystem: btrfs, zfs, glusterfs, ceph}
\cvlistitem{System image: Docker, Packer}
\cvlistitem{Containers: Create and maintain docker stack (compose|cloud)}

\subsection{DevOps}
\cvlistitem{Provisionning: Create and maintain Ansible playbooks and roles}
\cvlistitem{Cloud: OpenStack, AWS}
\cvlistitem{CI/CD: Git, gitlab-ci, github}
\cvlistitem{Git: Pre/Post-hooks, submodules, subtree}
\cvlistitem{Stabilisation of the deployment using several stage dev/testing/production}
\cvlistitem{Monitoring: ELK, Grafana, Prometheus, Nagios, Munin}
\cvlistitem{Monitoring application and system in a ELK stack Elasticsearch, Logstash, Kibana}
\cvlistitem{Monitoring network devices with sflow-rt, telegraf, influxdb, grafana}

\subsection{Scripting / Coding}
\cvlistitem{Software Development: TDD, SOLID}
\cvlistitem{Team/Project: Agile, Scrum, Kanban}
\cvlistitem{Scripting: Bash, Python, Perl}
\cvlistitem{Development of features with tests based on the specifications}
\cvlistitem{Test/Linter script of the code validity and code convention}
\cvlistitem{Load / stress test script}

\subsection{Documentation \& training}
\cvlistitem{Pair-programming \& reviews}
\cvlistitem{Write documentation in Sphinx/\LaTeX/Markdown}
\cvlistitem{Train and mentor teams to master technical problems}

\subsection{Run \& Security}
\cvlistitem{Incident response}
\cvlistitem{Security Auditing, backport fixes}
\cvlistitem{Troubleshoot critical applications}

\section{Experiences}

\tlcventry{2020}{2023}{DevOps}{ACA-CEGID}{https://www.cegid.fr}
{Paris}{
  \begin{itemize}%
    \item Monitoring (~1000 hosts) using M/Monit (scripts, services).
    \item Setup \& troubleshoot network config and issues (ip, route, vpn, firewall).
    \item Develop \& debug ansible roles (idempotent, tests, molecule).
    \item Migrate legacy layout ext4+lvm to zfs (poc + migration).
    \item Develop script to calculate real uncompressed used space (zfs, bash).
    \item Manage and maintain a cluster of zfs backups servers (ansible, zfs, bash).
    \item Harden linux config following ANSSI security guidelines (ansible, bash).
    \item Incident management and on-call response.
    \item Create and maintain documentation and process.
    \item Centralization of logs in elk (filebeat).
    \item Setup gitlab-ci and migrate ansible to use it.
    \item Environment Tech :
      \begin{itemize}%
        \item OS : Debian 10-11 / RedHat 7-8
        \item Cloud : VmWare
        \item EDI : NeoVim
        \item Technologies : Git, Ansible
        \item Server: PostgreSQL 9-10-11, Apache, Groovy, Java
      \end{itemize}
  \end{itemize}}

\vskip 2cm

\tlcventry{2017}{2020}{DevOps}{Orange-HebEx}{http://www.orange.fr}
{Bagnolet / Sophia-antipolis}{
  \begin{itemize}%
    \item Work with SCRUM and jira.
    \item Prototype vm (Vagrant, libvirt, virtualbox, Ansible).
    \item Create ansible role with  Molecule tests.
    \item Create ansible role freeradius.
    \item Create ansible role ldap (with proxy support).
    \item Create ansible role systemd-network (+yaml net config).
    \item Create ansible role zsh-prompt.
    \item Create ansible playbooks for sytem provisioning.
    \item Create ansible playbooks for application provisioning.
    \item Dev of a script to test multipath (bash).
    \item Dev of cluster vm for docker swarm testing with Ansible / Vagrant.
    \item Create docker image specialised for ci/cd with gitlab-ci.
    \item Dev of script for automatised packaging RPM (on top of MOCK).
    \item Backport / maintenance patchs for keepalived (C).
    \item Packaging / maintenance of management script for keepalived (bash / python / rcs).
    \item Packaging / maintenance of management script for haproxy (bash / python / rcs).
    \item Packaging missing software for centos7 en RPM (snimpy, colordiff, etc).
    \item Dev script of to manage IRQ of NIC on specific core of a CPU (bash / python / irqbalance).
    \item Benchmark linux firewall, depending on number of IRQ/Core with several NIC / driver.
    \item Dev ansible playbook to test openstack platform.
    \item Create base image for centos7, ubuntu14, ubuntu16 (packer / virtualbox|qemu).
    \item Create parsing script to convert scan snmp to ansible inventory (ini / python).
    \item Create smoke test script pour OpenStack.
    \item Create base system base image centos7, ubuntu14, ubuntu16 (packer / virtualbox|qemu) for OpenStack.
    \item Create parsing snmp to create ansible inventory (ini / python).
    \item Environment Tech :
      \begin{itemize}%
        \item OS : Gentoo / Ubuntu LTS Server (12.04 / 14.04 / 16.04) / CentOS 7.
        \item Cloud : OpenStack
        \item EDI : NeoVim.
        \item Technologies : Vagrant, LibVirt, Python, Git, Ansible, Molecule
        \item Server: keepalived, haproxy, quagga
      \end{itemize}
  \end{itemize}}

\vskip 2cm

\tlcventry{2016}{2017}{DevOps}{Display-Interactive}{http://www.ugo-ife.com/}
{Montrouge / Xiamen}{
  \begin{itemize}%
    \item Work with SCRUM and jira.
    \item Dev script to build vm image (bash, packer, virtualbox, qemu).
    \item Dev script to deploy on bare metal testing server (bash, qemu).
    \item Dev script to provision test server (bash, nginx, jplayer).
    \item Setup of raspberry's lab (*100) for load-tests (chef-serveur, chef-client, python, bash).
    \item Customisation of the Raspbian base image (kernel, services, drivers).
    \item Maintain and upgrade of chef recipes.
    \item Dev script of vm images manipulation from server or AWS bucket S3 (Python).
    \item Moving to remote site (Xiamen, China) and work (Admin + debug) on plane.
    \item Setup of Debian package depot for with GPG signature.
    \item Packaging of applications in deb format.
    \item Technical Environment :
      \begin{itemize}%
        \item OS : Gentoo / Ubuntu LTS Server (14.04 / 16.04), Raspbian.
        \item Cloud : AWS
        \item EDI : NeoVim.
        \item Technologies : PHP, NodeJs, Python, Git, Bash, git.
      \end{itemize}
  \end{itemize}}

\vskip 2cm

\tlcventry{2015}{2016}{DevOps}{WedZem}{WedZem.com}
{Paris}{
  \begin{itemize}%
    \item Refactoring of a WordPress's template (less, Bootstrap).
    \item Create container's web stack (docker-compose).
    \item Admin of dev/test/prod vm in a physical server (Proxmox).
    \item Maintain projects and followup (Git, GitLab).
    \item Technical Environment :
      \begin{itemize}%
        \item OS : Gentoo / Debian 8.
        \item Cloud : AWS
        \item Database : Mysql 5.5.
        \item EDI : Vim, Netbeans, Mysql Workbench.
        \item Technologies : PHP, JS, SQL, Py, Git, Bash, git.
      \end{itemize}
  \end{itemize}}

\vskip 2cm

\tlcventry{2013}{2015}{Developer}{Starpass}{BdMultimédia}
{Paris}{
  \begin{itemize}%
    \item Setup SCRUM to the team.
    \item Setup a git SCM, using 3 branch unstable / testing / stable.
    \item Dev snapshot script to help monitoring the migration to the SCM.
    \item Dev script to create / manage Linux user with env, tests and doc.
    \item Dev script to deploy, local, and remote with several tests.
    \item Dev script to test web-app, discover link, check HTTP status and timings.
    \item Dev script to audit PHP/JS code, find useless, encoding, path, include, indentation.
    \item Training of Agile development, and docs.
    \item Setup cygwin, for non-unix machine.
    \item Create schema (merise) of a existing database.
    \item Refactoring / versioning of DB (structure) and upgrade with scripts.
    \item Environment Tech :
      \begin{itemize}%
        \item OS : Debian 6 / 7.
        \item Database : Mysql 5.5.
        \item EDI : Vim, Netbeans, Mysql Workbench.
        \item Technologies : PHP, JS, SQL, Py, Git, Bash, git.
      \end{itemize}
  \end{itemize}}

\vskip 1cm
\vskip 5cm

\tlcventry{2012}{2013}{Developer}{Renault Retail Group}{Purjus}
{Paris}{
  \begin{itemize}%
    \item Create centralised platform http://renault-retail-group.fr.
    \item Create 7 dedicated regional spaces, like http://paris.renault-retail-group.fr/.
    \item Create a database using MERISE method.
    \item Create a collaborative dev platform, using svn and trac.
    \item Create UML diagram, and dev them in the projet.
    \item Create a testing platform.
    \item Managing a SVN depot, with 3 branches: unstable / testing / stable.
    \item Managing feature and bugfix branches in SVN.
    \item Dev feature following the Joomla framework.
    \item Creating mysql view.
    \item Environment Tech :
      \begin{itemize}%
        \item OS : Debian, freeBSD.
        \item Database : Mysql 5.5.
        \item Framework : Joomla.
        \item EDI : Eclipse, Netbeans, vim, mysql workbench.
        \item Libraries : sh404SEF, JCE.
        \item Technologies : PHP, JS, SQL, Py, SVN.
      \end{itemize}
  \end{itemize}}

\vskip 1cm

\tlcventry{2010}{2012}{Developer}{Renault Paris}{Purjus}
{Paris}{
  \begin{itemize}%
    \item Dev web on the project (PHP) : http://renaultparis.fr
    \item Dev of CRUD module to manage leads on the back-end.
    \item Dev information form in the front-end.
    \item Dev module to manage stock on the back-end.
    \item Create a SVN platform.
    \item Environment Tech :
      \begin{itemize}%
        \item OS : Debian, freeBSD.
        \item Database : Mysql 5.5.
        \item Framework : Joomla.
        \item EDI : Eclipse, Netbeans, vim.
        \item Libraries : sh404SEF, JCE.
        \item Technologies : PHP, JS, SQL, Py, SVN.
      \end{itemize}
  \end{itemize}}

\vskip 1cm

\tlcventry {2008}{2010}{Developer}{KP1}{GFI}
{Avignon}{
  \begin{itemize}%
    \item Dev computation engine based on formulas.
    \item Create and manage a database to store some params.
    \item Mise un place d'un cache objet Jcs.
    \item Dev test suite for the project with jUnit.
    \item Environnement Tech :
      \begin{itemize}%
        \item OS : Debian, Windows Xp, Windows 2003 Server, VMWare.
        \item Bases de données : SQL Server 2005
        \item Framework : JDK 1.5,  Struts 1.x.
        \item EDI : Vim, Eclipse 3.4.1 Ganymede, NetBeans 6.1
        \item Librairies : Tiles, Validator, Jep, Jcs, jUnit.
        \item Technologies : JAVA, Java Script, CSS, JSP, CVS.
      \end{itemize}
  \end{itemize}}

\vskip 1cm
\tlcventry {2007}{2008}{Sysadmin}{Mairie de Marseille}{Computacenter}
{Marseille}{
  \begin{itemize}%
    \item Managing testing and production server.
    \item Managing tests and services check.
    \item Dev and manage load test.
    \item Backup server and database.
    \item Environment Tech :
      \begin{itemize}%
        \item OS : Debian, Win2003, RedHat Entreprise, Ubuntu.
        \item Database : Oracle 9.x, MySQL 4.x, Sql Server 2005.
        \item EDI : Vim, NotePad++.
        \item Technologies : SSH, Bash linux et windows.
      \end{itemize}
  \end{itemize}}

\vskip 1cm
\tlcventry {2005}{2007}{Developer}{Liligo}{Findworks Technologies}
{Paris}{
  \begin{itemize}%
    \item Dev web on the project : http://www.liligo.com/
    \item Dev parsing script with server-side (JS).
    \item Dev scrapping script for website (PERL).
    \item Dev XHTML/css following graphical chart.
    \item Study on SEO.
    \item Quality control and load test.
    \item Environment Tech :
      \begin{itemize}%
        \item OS : Debian, WinXP.
        \item Database : MySQL 4,x
        \item Framework : JDK 1,4.
        \item EDI : Eclipse 3,2 Web Tools Platform.
        \item libraries : hibernate.
        \item Technologies : SSH, JAVA, JSP, Java Script, CSS, xHTML, PERL.
      \end{itemize}
  \end{itemize}}

\vskip 1cm

\section{Training}
\tlcventry{2008}{2009}{J2EE \& .NET training}{}{}{CESI school}{Aix-en-Provence}{}
\tlcventry{2005}{2007}{BTS Information Systems}{}{Application Developer Option}{Ecole Charlotte Grawitz}{Marseille}{}
\tlcventry{2002}{2004}{DEUG de psychology}{}{}{Faculté de lettres}{Aix-en-Provence}{}
\tlcventry{2001}{2002}{Baccalauréat STI}{}{Electronic Option}{Lycée Antonin Artaud}{Marseille}{}

\section{Languages}
\cvlanguage{Anglais}{Advanced}{Regular practice.}
\cvlanguage{Spanish}{school}{Basic understanding.}

\section{Hobbies}
\cvhobby{Strategy games}{go, mtg}
\cvhobby{Open Source Enthusiast}{Several active project on Github}
\cvhobby{Others}{Travel, Music, Reading}

\clearpage
\end{document}

% vim: set ft=tex ts=2 sw=2 tw=80 foldmethod=marker et :
